\begin{thebibliography}{X}
	
	\bibitem{B15} \textsc{Hsu, Pei-Hsien}, \textsc{Huang, Sheng-Yang} y \textsc{Lin, Bao-Shuh} "Smart-Device-Based Augmented Reality (SDAR) Models to Support Interior Design: Rethinking “Screen” in Augmented Reality", National Chiao Tung University, Taiwan
	
	\bibitem{B01} \textsc{Montes de Oca, Irina} y \textsc{Risco, Lucía},
	"Apuntes de diseño de interiores",
	\textit{Principios básicos de escalas. espacios, colores y más}, primera edicion,
	ECOE EDICIONES
	
	\bibitem{B02} "FAQ for designers", \textit{Whats is Interior Design}, Interior Design Legislative Coalition of Pennsylvania (IDLCPA), 2011. Recuperado de: https://www.idlcpa.org/forms/resources/FAQforDesigners.pdf
	
	\bibitem{B26} Kathryn, T.,(2000), feng shui habitación por habitación (12ª ed.). ES, Urano.	
	
	\bibitem{B24} Harris, C., (2006), dictionary of architecture and construction (4ª ed.). New York, EU, McGraw-Hill.
	
		
	\bibitem{B13} \textsc{Viola, Romina} (11 de mayo de 2016), "Cómo Elegir la Paleta de Colores", \textit{Parte I: Entender el Color}. Spanish Community Champion | Piktochart. [Online] Recuperado de: https://piktochart.com/es/blog/como-elegir-la-paleta-de-colores-parte-entender-el-color/
	
	
	
	\bibitem{B04} \textsc{Siltanen, Sanni} "Diminished reality for augmented reality interior design", Springer-Verlag Berlin Heidelberg 2015. Publicado el: 30 de Noviembre de 2015. DOI: 10.1007/s00371-015-1174-z
	DOI 10.1007/978-3-319-54502-8
	
	\bibitem{B05} \textsc{Donggang Yu1, Jesse Sheng Jina},
	"A Useful Visualization Technique: A Literature Review for Augmented Reality and its Application, limitation and future direction", primera edicion,
	School of Design, Communication and Information Technology, The University of Newcastle, Callaghan, NSW 2308, Australia
	
	
	
	\bibitem{B27} \textsc{Furht, Borko} "Handbook of Augmented Reality",Department of Computer and Electrical Engineering and Computer Science,Florida Atlantic University (),Glades Road 777 33431 Boca Raton, Florida USA,DOI 10.1007/978-1-4614-0064-6
	
	\bibitem{B22} \textsc{Peddie, Jon} "Augmented Reality Where we will all live", Springer International Publishing AG 2017. Publicado el: 19 de Abril del 2017. DOI 10.1007/978-3-319-54502-8 
	
	\bibitem{B09} \textsc{Monteiro, Paula} and \textsc{Nagele, Aleksandra}, "Wikitude" \textsc{Company Overview}, Recuperado de: https://s3-eu-west-1.amazonaws.com/wikitude-web-hosting/static-website/2017/07/01728364/Media+page+presentation+-+Wikitude.pdf
	
	
	
	\bibitem{B16} "Wikitude Products", 29 de agosto de 2018. Recuperado de: https://www.wikitude.com/products/wikitude-sdk/
	
	
	\bibitem{B20} "ARKit Developer", 2 de Septiembre de 2018. Recuperado
	https://developer.apple.com/arkit/
	
	\bibitem{B21} "ARKit Documentation", 3 de Septiembre de 2018. Recuperado
	https://developer.apple.com/documentation/arkit/
	
	
	\bibitem{B12} \textsc{Grahn, Ivar}, "The Vuforia SDK and Unity3D Game Engine", \textit{Evaluating performanceo on Android Devices}. Linköping University | Department of Computer and Information, Science Bachelor thesis, 16 ECTS, Computer Science 2017, LIU-IDA/LITH-EX-G–17/059–SE
	
	
	\bibitem{B14} "ARCore Overview", 2 de agosto de 2018. Recuperado de: https://developers.google.com/ar/discover/
	\\
	
	
	%
	
	\bibitem{B03} \textsc{Takahashi, Yoshiyuki} y \textsc{Mizumura, Hiroko},
	"Augmented Reality Based Environment Design Support System for Home Renovation", Toyo  University, Department of Human Environment Design, Faculty of Human Life Design, Oka 48-1, Asaka-shi, Saitama, 351-8510 Japan 
	
	
	
	\bibitem{B06} \textsc{Buerli, Mike} and \textsc{Misslinger, Stefan}, "Introducing ARKit", \textit{Augmented Reality for iOS. Session 602} Recuperado de: https://devstreaming-cdn.apple.com/videos/wwdc/2017/602pxa6f2vw71ze/602/602
	\_introducing\_arkit\_augmented\_reality\_for\_ios.pdf?dl=1
	
	\bibitem{B07} \textsc{Strandmark, Petter}, "Augmented reality with the ARToolKit", Recuperado de: http://www.maths.lth.se/matematiklth/personal/petter/rapporter/artoolkit4.pdf
	
	\bibitem{B08} \textsc{Fuster Andújar, Francisco de Asís}, "Aplicación Android de realidad aumentada para mostrar imágenes históricas de lugares turísticos de interés", Tesis. Escola Tècnica Superior d’Enginyeria Informàtica Universitat Politècnica de València, Valencia, España, 2014.
	
	
	\bibitem{B10} \textsc{Asrul Sani, Nisfu}, "Google ARCore", Lab Langit 9 - PENS 20-22 de noviembre de 2017. Recuperado de: http://dhoto.lecturer.pens.ac.id/training/arcore/SONI-ARCORE.pdf
	
	\bibitem{B11} \textsc{Kaleda, Yuliya}, "Add Reality to App with ARCore". Recuperado de: https://downloads.ctfassets.net/2grufn031spf/7AyZDCxxIs0AoOgwOsy0m4/26f89f9d2
	f346dd3c6a55f5d3e2de96e/Yuliya\_Kaleda\_Add\_Reality\_To\_App\_with\_ARCore.pdf
	

	
	
	
	\bibitem{B18} "OpenGL Documentation", 30 de agosto de 2018. Recuperado de:
	https://www.opengl.org/documentation/
	
	\bibitem{B19} "OpenGL Glut", 30 de agosto de 2018. Recuperado
	https://www.opengl.org/resources/libraries/glut/spec3/spec3.html
	
    
	
	\bibitem{B23} "Vuforia Supported-devices", 4 de Septiembre de 2018. Recuperado
	https://library.vuforia.com/articles/Solution/vuforia-fusion-supported-devices.html
	
	\bibitem{B25} Medina, V. E., (2003). Forma y composición en la arquitectura descontructivista (Tesis doctoral). Escuela Técnica Superior de Arquitectura de Madrid, Madrid, Esp.
	
	
	\bibitem{B28} "The new power tool for home improvement", 22 de Octubre del 2018. Recuperado https://canvas.io/
	\bibitem{B29} "Amazon.com.mx" 22 de Octubre. Recuperado  de  2018 https://www.amazon.com.mx/ 
	\bibitem{B30} "Fingo. Furniture. Try before you buy!" 22 de Octubre 2018 https://itunes.apple.com/us/app/fingo.vybor-mebeli-katalog/id845105741
	\bibitem{B29} "Amazon.com.mx" 22 de Octubre. Recuperado  de  2018 https://www.amazon.com.mx/ 
	
	
\end{thebibliography}
